---
title: "GIS"
author: "MP"
date: "20/11/2021"
output: html_document
---
# PURPOSE
Worked example using the OSRM package to calculate distance and travel time, then ggplot to map the results.


# SETUP
## Attach packages
```{r}
library(osrm)
library(ggplot2)
library(ggspatial)
library(tidyr)
library(sf)
library(dplyr)
```


## Define constants 
It's important to note here that co-ords c&p from Google are lat/long, whereas osrm wants long/lat 
```{r}
coords_victoria_house <- c(0.19433553692634412,52.18514306078607)
```




# VISUALISE
## Isometric (equal distance) from Victoria House by road
### Calculate
```{r}
isometric_iph <- osrmIsometric(loc = coords_victoria_house,breaks = c(1000,2000))
```


# Map
```{r}
# I'd like the distances to display on the legend as two discrete values, so factorise them
iso_2_map <- isometric_iph %>% 
  mutate(max = factor(max))

map_iph_isometric <- ggplot(iso_2_map) +
  annotation_map_tile("cartolight") +
  geom_sf(aes(geometry = geometry, fill = max),alpha = 0.1) +
  scale_fill_discrete(name = "Distance by road (meters)") +
  theme_void()

map_iph_isometric
```


## Isochrone (equal travel time) from Victoria House by car
### Calculate
```{r}
isochrone_iph <- osrmIsochrone(loc = coords_victoria_house,
                               breaks = c(10,20),
                               osrm.profile = "car"
                               )
```


# Map
```{r}
# I'd like the distances to display on the legend as two discrete values, so factorise them
iso_2_map <- isochrone_iph %>% 
  mutate(max = factor(max))

map_iph_isochrone <- ggplot(iso_2_map) +
  annotation_map_tile("cartolight") +
  geom_sf(aes(geometry = geometry, fill = max),alpha = 0.1) +
  
  scale_fill_discrete(name = "Travel time by car (minutes)") +
  
  theme_void()

map_iph_isochrone
```







